Cognate Priming: Report

### 2023-10-31 docs/report.qmd
Update targets progress

---
title: "Cognate Priming: Report"
format: html
---

```{r setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
# load objects
targets::tar_config_set(store = here::here("_targets"),
						script = here::here("_targets.R"))
targets::tar_load_globals()

>>>>

---
---

```{r setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
# load objects
targets::tar_config_set(store = here::here("_targets"),
						script = here::here("_targets.R"))
